The expected shape of the Milky Way's Dark Matter halo

### 2019-02-13 Paper/paper.tex
edit

We quantify this effect by plotting the axial ratios $b/a$, $c/a$,
$c/b$ and the triaxiality $T\equiv \frac{1-b/a}{1-c/a}$ as a
function of radius. 
As a representative sample of this
relations, we show on figure \ref{fig:triaxial_radius} the evolution, for
a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.

\begin{figure}
\centering
{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
\caption{Radial profile for the axial ratios and the triaxiality parameter
  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
  Radial profile was sampled at
  redshift 0 and there are two sets of lines showing MHD and DM-only
  versions of the axial ratios profile} \label{fig:triaxial_radius}
\end{figure}

>>>>

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/halo16.png}}
\caption{Radial profile for the axial ratios and the triaxiality parameter
  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
  Radial profile was sampled at
  redshift 0 and there are two sets of lines showing MHD and DM-only
  versions of the axial ratios profile} \label{fig:triaxial_radius}
\end{figure*}

We quantify this effect by plotting the axial ratios $b/a$, $c/a$,
$c/b$ and the triaxiality $T\equiv \frac{1-b/a}{1-c/a}$ as a
function of radius. 
As a representative sample of this relations we show on figure
\ref{fig:triaxial_radius} the radial trends for an specific halo at
the highest resolution both for DM and MHD simulations.
The continouse lines corresponds to the DM simulation and shows how
the inner part of the halo $r\approx 1$\kpch has values of 
$b/a=0.5$, $c/a=0.5$ while at the virial radius the same
quantities increase to $b/a=0.9$, $c/a=0.6$; in turn the triaxiality
decrease from $T\approx 1.0$\kpch to $T\approx=0.4$.
